### 2016-09-11 draft/draft.tex
Updates

\maketitle
\makedeclaration

@@

Docker\cite{1docker} is a platform which
allows the creation of self-contained virtual environments for software
development, to mitigate arbitrary local differences between development
environments. It was an essential part of the development process as
Eris's tooling leverages Docker heavily to deploy blockchain
instances.\\
Bash shell scripts (\textbf{see Appendix X}) were constructed by the
author in order to automate processes such as hydrating the local
terminal environment with variables required to run the blockchain, or
booting the Docker virtual machine and the local blockchain instance.

@@

\begin{longtable}[]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.04\columnwidth}\raggedright\strut
ID\strut
\end{minipage} & \begin{minipage}[b]{0.64\columnwidth}\raggedright\strut
Functional Requirements\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\raggedright\strut
Category\strut
\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedright\strut
MoSCoW Priority\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ1\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Users should be able to sign up by providing simply a username, password
and, optionally, an email address\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Account registration\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Must\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ2\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Users should be able to login using a username and password\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Login\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Must\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ3\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Any team member should be able to register a task for their team on the
network, by specifying team members involved\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Tasks\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Must\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ4\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Any team member is able to view both outstanding and completed
tasks\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Tasks\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Must\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ5\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
If user is not a member of a team, they should be able to start a new
team by adding other members via their usernames\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Team\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Must\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ6\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Upon resolution the task reward should be added to the participants'
scores automatically and immediately\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Tasks\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Must\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ7\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Users should be able to issue a request to join an existing team or
create a new one upon signup\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Account registration\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ8\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Users should receive sign up confirmation to verify email address\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Account registration\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ9\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Any team member should be able to opt out of a task they were entered
for if they are not in fact involved\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Tasks\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ10\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Each team member can see how many other members have completed a given
task without identities being revealed in the process\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Tasks\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ11\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Individuals should be able to provide public links to their completed
tasks and general profile\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Tasks\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ12\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Users should be able to see their team's current global ranking\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Team\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ13\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Users should be able to recover their password if they have forgotten
it\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Login\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ14\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Users should be able to view incomplete tasks their involved in and past
completed tasks\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Tasks\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ15\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Users should be able to upload attachments related to their tasks\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Tasks\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ16\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Tasks should automatically resolve to status ``Complete'' once all
participants have completed them\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Tasks\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ17\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Users should be able to edit their account details after signing up
(email address, password);\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
User\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ18\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Users should be able to delete their account\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Settings\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ19\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
An individual can request help for a task from other task
participants\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Team\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Could\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ20\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Members may offer help to the rest of the team without a specific
request being present, to speed up any potential rendez-vous\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Team\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Could\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ21\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Once a rendez-vous occurs, the parties involved should be able to chat
with each other\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Team\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Could\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ22\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Team members should be notified via a mobile alert if a help request
affects them\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Team\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Could\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ23\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Users could be able to upload a profile picture\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
User\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Could\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\raggedright\strut
FRQ24\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright\strut
Users should be able to mute help request and help offer
notifications\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
Settings\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
Could\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\begin{figure}[htbp]
\centering
\includegraphics{}
\caption{Functional Requirements}
\end{figure}

\begin{longtable}[]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.05\columnwidth}\raggedright\strut
ID\strut
\end{minipage} & \begin{minipage}[b]{0.63\columnwidth}\raggedright\strut
Non-Functional Requirements\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
Category\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
MoSCoW Priority\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.05\columnwidth}\raggedright\strut
NFRQ1\strut
\end{minipage} & \begin{minipage}[t]{0.63\columnwidth}\raggedright\strut
A User who is not logged in is prevented from accessing the app\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
Security\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
Must\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright\strut
NFRQ2\strut
\end{minipage} & \begin{minipage}[t]{0.63\columnwidth}\raggedright\strut
The system shall store all user passwords in the blockchain in an
encrypted format\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
Security\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
Must\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright\strut
NFRQ3\strut
\end{minipage} & \begin{minipage}[t]{0.63\columnwidth}\raggedright\strut
The app should provide offline sync, saving any state changes made
during a period of no-connection\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
Persistence\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright\strut
NFRQ4\strut
\end{minipage} & \begin{minipage}[t]{0.63\columnwidth}\raggedright\strut
A team member should be able to signal a task as complete within a
maximum of 1\textasciitilde{}2 UI interactions\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
Tasks\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright\strut
NFRQ5\strut
\end{minipage} & \begin{minipage}[t]{0.63\columnwidth}\raggedright\strut
The system should accomodate for at least 1,000 teams\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
Capacity\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright\strut
NFRQ6\strut
\end{minipage} & \begin{minipage}[t]{0.63\columnwidth}\raggedright\strut
The system should accomodate for at least 100,000 tasks\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
Capacity\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright\strut
NFRQ7\strut
\end{minipage} & \begin{minipage}[t]{0.63\columnwidth}\raggedright\strut
The system should log in a user within approximately 5 seconds\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
UX\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright\strut
NFRQ8\strut
\end{minipage} & \begin{minipage}[t]{0.63\columnwidth}\raggedright\strut
The system shall respond to any interaction in no more than 10
seconds\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
UX\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
Should\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\begin{figure}[htbp]
\centering
\includegraphics{}
\caption{Non-Functional Requirements}
\end{figure}

@@

Use cases were constructed in parallel with the initial UI sketches,
thus helping to visualise the flow of user-system interactions.\\
Figure 3.4 below represents an overview of the uses cases that
were constructed, while the detailed use cases can be reviewed in Appendix B.

\begin{longtable}[]{@{}llll@{}}
\toprule
ID & Use Case & Primary Actor & Secondary Actor\tabularnewline
\midrule
\endhead
UC1 & Signup & User & System\tabularnewline
UC2 & Login & User & System\tabularnewline
UC3 & AddTask & User & System\tabularnewline
UC4 & ViewTasks & User & System\tabularnewline
UC5 & TaskComment & User & System\tabularnewline
UC6 & OptOutOfTask & User & System\tabularnewline
UC7 & CheckTaskCompletion & User & System\tabularnewline
UC8 & ExternalLinkToTask & User & System\tabularnewline
UC9 & CreateTeam & User & System\tabularnewline
UC10 & CheckTeamScore & User & System\tabularnewline
UC11 & RequestHelp & User & System\tabularnewline
UC12 & OfferHelp & User & System\tabularnewline
UC13 & MuteNotifications & User & System\tabularnewline
UC14 & EditAccount & User & System\tabularnewline
UC15 & SetProfilePicture & User & System\tabularnewline
UC16 & DeleteAccount & User & System\tabularnewline
UC17 & AttachTaskFile & User & System\tabularnewline
\bottomrule
\end{longtable}

\begin{figure}[htbp]
\centering
\includegraphics{}
\caption{Use Case Overview}
\end{figure}

@@

The design of the system's architecture started with creating a simple
deployment diagram (Figure 3.5), which provided a high-level view of
the system's required components and the roles they would play.\\
Establishing a high-level understanding of what the system required to
provide proficient communication between any client application and the
Tendermint blockchain was an essential aspect of the initial design
phase. Decoupling the system's functionality from the specific
implementation with which the system may be represented to a user was a
crucial provision to ensure maximum reusability and compatibility of the
system, therefore following the common software engineering mantra of
\emph{``program to an interface, not an implementation''}\cite{1programtointerface}.
Within the context of the web, the most appropriate form to follow this
approach was by developing a RESTful\cite{1rest} API, thus providing a
uniform interface of data endpoints, regardless of the client requesting
said data.

@@

The blockchain's factory contracts were a straightforward undertaking,
both in regards of design and implementation, as their only role was to
return a new instance of the contract, which would then be handled by
the associated manager contracted. This meant the factory contract would
simply contain its required fields and a constructor, as shown in
\textbf{Appendix X}.

Solidity's inability to process an externally passed JavaScript object
is nicely exemplified here, due to the sheer verbosity of the
constructor function. While a task could be encapsulated as a single
object and therefore passed as a single parameter within the client- and
server-side JavaScript applications, the object had to be split into its
constituent fields by the NodeJS server before it could be handed to the
blockchain. This created what is commonly referred to as a ``code
smell''\cite{tufano2015codesmell}, by forcing the author to
implement an excessively large amount of parameters. This made both the
factory contracts themselves and the server's methods that deconstructed
the initial JavaScript object for the blockchain brittle, as any change
to a factory contract's fields had cascading effects throughout the API,
thus creating an unnecessary opportunity for bugs to appear if
refactoring was not done in a meticulous manner.

@@

An essential function of the NodeJS server is to act as data handler,
thus defining the way data has to be formatted to flow between the React
Native client app and the blockchain. As the server implements an API
interface which should be suitable for any client-side implementation,
the data transformations required took the form of translating
JavaScript objects coming from the client to a hexadecimal format in
order to adhere to Solidity's \texttt{bytes32} type, for the reasons
that were laid out in chapter 3. This was achieved by use of a
``pipeline'' function.\\
The pipeline function was defined within the utility module
\texttt{chainUtils.js} as
\texttt{marshalForChain(\textless{}data-object\textgreater{})}, which
can be reviewed in full in \textbf{Appendix X}. The function takes its
\texttt{\textless{}data-object\textgreater{}} parameter, identifies the
type of each object property (e.g.
\texttt{Array.isArray(\textless{}property\textgreater{})}) and
transforms it into a string representation of itself. Representing all
of the \texttt{\textless{}data-object\textgreater{}}s properties as
strings in an intermediate step is necessary in order to utilise the
\texttt{eris-wrapper} library module's
\texttt{str2hex(\textless{}string\textgreater{})} (string-to-hex)
function, which accepts a string as a parameter and transforms it into a
32-byte hexadecimal string. \texttt{str2hex} is therefore the final step
in the \texttt{marshalForChain} function, preparing each of the object's
properties to be fed into the blockchain.

@@

\section{5.5 Coverage}\label{coverage}

\textbf{TODO: final coverage report will be added when implementation is
complete}

@@

\appendix
\chapter{Additional Diagrams}

\begin{figure}[htbp]
\centering
\includegraphics{../diagrams/signupSeqDiagram.png}
\caption{Sequence of events for a ``Signup'' action}
\end{figure}

\begin{sidewaysfigure}[ht]
\centering
\includegraphics{../diagrams/contractsClassDiagram.png}
\caption{A full Class diagram for the system's smart contracts}
\end{sidewaysfigure}

\chapter{Use Cases}

\include{use-cases}

\chapter{System Manual}
\section{Installation}\label{installation}

\paragraph{Dependencies}\label{dependencies}

The following dependencies are required to run a local development
instance of QuantiTeam's
\href{https://github.com/tendermint/tendermint}{Tendermint} blockchain:
- \href{https://www.docker.com/}{Docker} CLI - \texttt{docker} (\&
\texttt{docker-machine} on OSX).\\
- \href{https://erisindustries.com/}{Eris} CLI - \texttt{eris} provides
a wrapper and toolchain around the Tendermint blockchain and is used
extensively.\\
- \href{https://nodejs.org/en/}{Node.js} - v4.x upwards.\\
- \href{https://www.npmjs.com/}{NPM} - QuantiTeam relies on NPM scripts
to run tests and various other tasks.

To install the project's Node.js dependencies, ensure your present
working directory (\texttt{pwd}) is \texttt{quantiteam/chain} and run:

\begin{verbatim}
npm install
\end{verbatim}

\paragraph{Setting up}\label{setting-up}

First, let's move into QuantiTeam's API directory with the following
command:

\begin{verbatim}
cd chain
\end{verbatim}

Creating a local dev \texttt{simplechain}:\\
- Automatically: Run \texttt{simplechain.sh} in the repository's root
directory, which should start logging the chain's activities after
setup.\\
- Manually: Follow Eris's brief
\href{https://docs.erisindustries.com/tutorials/chain-making/}{tutorial}.

\subsection{Running a local development
chain}\label{running-a-local-development-chain}

Assuming we now have a functioning \texttt{simplechain} instance, let's
boot it up and configure some local environment variables. In the repo's
root directory run the following two shell scripts:

\begin{verbatim}
. ./chain-up.sh; . ./envsetup.sh
\end{verbatim}

We can easily verify whether the \texttt{simplechain} instance is
running as expected by following its log output:

\begin{verbatim}
npm run chainlog
\end{verbatim}

\subsection{Running the Node.js chain
service}\label{running-the-node.js-chain-service}

Now that we have a local development chain running which we can interact
with, let's spin up the chain service which will act as our API router
to interface with the local chain itself.

\paragraph{Deploying contracts}\label{deploying-contracts}

First, let's compile and deploy our Solidity smart contracts in the
\texttt{contracts} directory:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# `$addr` should be defined from previously running `envsetup.sh`}
\KeywordTok{npm} \NormalTok{run compile -- }\OtherTok{$addr}
\end{Highlighting}
\end{Shaded}

Anytime a change is made to the smart contracts, \texttt{compile} should
be run to deploy these changes to the running \texttt{simplechain}
instance.

\paragraph{Running tests}\label{running-tests}

Next, we'll want to run QuantiTeam's test suite to ensure everything is
working as expected:

\begin{verbatim}
npm test
\end{verbatim}

This should also provide a coverage report once all unit tests have run.

\paragraph{Booting the service}\label{booting-the-service}

The chain service itself can be built \& booted simply with:

\begin{verbatim}
npm run build
\end{verbatim}

Anytime a change is made to the node server, \texttt{build} should be
run as it builds the new service container via \texttt{docker} and
replaces it with the previous one via \texttt{eris}.\\
Please refer to \texttt{package.json} for more detailed insights into
which shell commands each NPM script executes.

\subsection{API}\label{api}

QuantiTeam's API exposes the following HTTP endpoints:\\
- POST
\texttt{/upload} - Upload a task related file via
\texttt{multipart/form-data}.\\
- POST \texttt{/user/taken} - Check whether the the username in
\texttt{req.body.username} is already taken.\\
- POST \texttt{/user/signup} - Sign up a new user with the form data
passed in \texttt{req.body}.\\
- POST \texttt{/user/login} - Log in an existing user with the form data
passed in \texttt{req.body}.\\
- GET \texttt{/user/profile/:username} - Get the profile of the username
passed via \texttt{req.params.username}.\\
- GET \texttt{/tasks/:username} - Get the tasks of the username passed
via \texttt{req.params.username}.\\
- POST \texttt{/task} - Add a new task to the blockchain via the form
data passed in \texttt{req.body.task} for the username in
\texttt{req.body.username}.\\
- GET \texttt{/task/completed/:token} - Mark the task associated with
the token passed in \texttt{req.params.token} as completed. - GET
\texttt{/team/taken/:teamname} - Check whether the teamname passed as
\texttt{req.params.teamname} is already taken.\\
- POST \texttt{/team} - Add a new team to the blockchain via the form
data passed in \texttt{req.body.form}.\\
- GET \texttt{/team/:teamname} - Get the team profile for the teamname
passed as \texttt{req.params.teamname}.\\
- POST \texttt{/team/add-member} - Add a new member to a team with the
form data passed in \texttt{req.body.form}.

\subsection{Shutting down}\label{shutting-down}

To shut down the local chain and the \texttt{docker-machine} instance,
simply run:

\begin{verbatim}
. ./chain-down.sh
\end{verbatim}

\chapter{User Manual}

>>>>

@@

Docker\cite{1docker} is a platform which
allows the creation of self-contained virtual environments for software
development, to mitigate arbitrary local differences between development
environments. It was an essential part of the development process as
Eris's tooling leverages Docker heavily to deploy blockchain
instances.\\
Bash shell scripts (see Appendix F) were constructed by the
author in order to automate processes such as hydrating the local
terminal environment with variables required to run the blockchain, or
booting the Docker virtual machine and the local blockchain instance.

@@

\include{functional-requirements}

\include{nonfunctional-requirements}

@@

Use cases were constructed in parallel with the initial UI sketches,
thus helping to visualise the flow of user-system interactions.\\
The table below represents an overview of the uses cases that
were constructed, while the detailed use cases can be reviewed in Appendix B.

\begin{longtable}[]{@{}llll@{}}
\toprule
ID & Use Case & Primary Actor & Secondary Actor\tabularnewline
\midrule
\endhead
UC1 & Signup & User & System\tabularnewline
UC2 & Login & User & System\tabularnewline
UC3 & AddTask & User & System\tabularnewline
UC4 & ViewTasks & User & System\tabularnewline
UC5 & TaskComment & User & System\tabularnewline
UC6 & OptOutOfTask & User & System\tabularnewline
UC7 & CheckTaskCompletion & User & System\tabularnewline
UC8 & ExternalLinkToTask & User & System\tabularnewline
UC9 & CreateTeam & User & System\tabularnewline
UC10 & CheckTeamScore & User & System\tabularnewline
UC11 & RequestHelp & User & System\tabularnewline
UC12 & OfferHelp & User & System\tabularnewline
UC13 & MuteNotifications & User & System\tabularnewline
UC14 & EditAccount & User & System\tabularnewline
UC15 & SetProfilePicture & User & System\tabularnewline
UC16 & DeleteAccount & User & System\tabularnewline
UC17 & AttachTaskFile & User & System\tabularnewline
\bottomrule
\caption{Use Case Overview}
\end{longtable}

@@

The design of the system's architecture started with creating a simple
deployment diagram (Figure 3.2), which provided a high-level view of
the system's required components and the roles they would play.\\
Establishing a high-level understanding of what the system required to
provide proficient communication between any client application and the
Tendermint blockchain was an essential aspect of the initial design
phase. Decoupling the system's functionality from the specific
implementation with which the system may be represented to a user was a
crucial provision to ensure maximum reusability and compatibility of the
system, therefore following the common software engineering mantra of
\emph{``program to an interface, not an implementation''}\cite{1programtointerface}.
Within the context of the web, the most appropriate form to follow this
approach was by developing a RESTful\cite{1rest} API, thus providing a
uniform interface of data endpoints, regardless of the client requesting
said data.

@@

The blockchain's factory contracts were a straightforward undertaking,
both in regards of design and implementation, as their only role was to
return a new instance of the contract, which would then be handled by
the associated manager contracted.

Solidity's inability to process an externally passed JavaScript object
is nicely exemplified by the \texttt{Task.sol} factory contract (see Appendix F), due to the sheer verbosity of the
constructor function. While a task could be encapsulated as a single
object and therefore passed as a single parameter within the client- and
server-side JavaScript applications, the object had to be split into its
constituent fields by the NodeJS server before it could be handed to the
blockchain. This created what is commonly referred to as a ``code
smell''\cite{tufano2015codesmell}, by forcing the author to
implement an excessively large amount of parameters. This made both the
factory contracts themselves and the server's methods that deconstructed
the initial JavaScript object for the blockchain brittle, as any change
to a factory contract's fields had cascading effects throughout the API,
thus creating an unnecessary opportunity for bugs to appear if
refactoring was not done in a meticulous manner.

@@

An essential function of the NodeJS server is to act as data handler,
thus defining the way data has to be formatted to flow between the React
Native client app and the blockchain. As the server implements an API
interface which should be suitable for any client-side implementation,
the data transformations required took the form of translating
JavaScript objects coming from the client to a hexadecimal format in
order to adhere to Solidity's \texttt{bytes32} type, for the reasons
that were laid out in chapter 3. This was achieved by use of a
``pipeline'' function.\\
The pipeline function was defined within the utility module
\texttt{chainUtils.js} as
\texttt{marshalForChain(\textless{}data-object\textgreater{})}, which
can be reviewed in full in Appendix F. The function takes its
\texttt{\textless{}data-object\textgreater{}} parameter, identifies the
type of each object property (e.g.
\texttt{Array.isArray(\textless{}property\textgreater{})}) and
transforms it into a string representation of itself. Representing all
of the \texttt{\textless{}data-object\textgreater{}}s properties as
strings in an intermediate step is necessary in order to utilise the
\texttt{eris-wrapper} library module's
\texttt{str2hex(\textless{}string\textgreater{})} (string-to-hex)
function, which accepts a string as a parameter and transforms it into a
32-byte hexadecimal string. \texttt{str2hex} is therefore the final step
in the \texttt{marshalForChain} function, preparing each of the object's
properties to be fed into the blockchain.

@@

\section{5.5 Coverage}\label{coverage}
Test coverage reports were generated automatically following each execution of the API's test suite. A coverage summary is shown below, while the full report can be located as browsable collection of HTML files in the repository's \texttt{chain/test/coverage} directory. Appendix E shows the index page of these HTML reports to provide an overview.

\begin{lstlisting}
  35 passing (45s)

=============================== Coverage summary ===============================
Statements   : 90.64% ( 426/470 ), 4 ignored
Branches     : 56.49% ( 74/131 ), 5 ignored
Functions    : 97.12% ( 135/139 ), 1 ignored
Lines        : 91.22% ( 426/467 )
================================================================================
\end{lstlisting}

@@

\include{appendix}
